\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-09 fully-abstract-comp/popl2019/paper.tex
minor comments and eddits.

\input{../preamble}
% Paper specific redefinitions of commands
\renewcommand{\MemSeg}{\shareddom{MemSeg}}
\renewcommand{\Reg}{\shareddom{RegFile}}
\renewcommand{\RegName}{\shareddom{RegName}}
\renewcommand{\decInstr}[1]{\plainfun{decode}{#1}}
\renewcommand{\updPcAddr}[1]{\plainfun{updPc}{#1}}
\renewcommand{\linCons}[1]{\plainfun{linClear}{#1}}
\renewcommand{\nonExec}[1]{\plainfun{nonExec}{#1}}
\renewcommand{\perm}{\var{p}}
\renewcommand{\SealableCaps}{\shareddom{Sealables}}
\renewcommand{\Cap}{\shareddom{NatTok}}
\renewcommand{\rretc}{\mathrm{r}_{\mathrm{rcode}}}
\renewcommand{\rretd}{\mathrm{r}_{\mathrm{rdata}}}
\renewcommand{\comp}{\var{comp}}
\renewcommand{\memSatStack}[3][n]{\npair[#1]{#2} \in \typesetlr{S}(#3)}
\renewcommand{\memSatFStack}[3][n]{\npair[#1]{#2} \in \typesetlt{F}(#3)}
\renewcommand{\Worlds}{\World_{\mathrm{call\ stack}}}

@@

\newcommand{\trgcm}{\textsc{LCM}}
\newcommand{\srccm}{\textsc{oLCM}}
\newcommand{\extend}[1]{}

@@

\todo[inline]{Add itemized contributions (see comments). Outline?}
% The main contributions of this paper are (1) \stktokens{} a calling convention that uses linear capabilities to provably secure local state encapsulation and well-bracketed control flow, and (2) a novel proof technique that we call fully-abstract overlay semantics.

% Presents the first formal model of a capability machine with linear capabilities (Section 2)
% Presents a calling convention called \stktokens{} that provably guarantee local state encapsulation and well-bracketed control flow (Section 3)
% Presents a novel proof technique that we call fully-abstract overlay semantics. (Section 4-5)

% \begin{itemize}
% \item 
% \end{itemize}

%\paragraph{Outline} Blabla

@@

%%% Seals
Any reasonable capability machine needs a way to setup boundaries between security domains as well as a way to cross the boundaries in a way where each domain retains their authority.
%The M-Machine~\citep{Dally1997Memo59} inspired capability machine in \citet{skorstengaard_reasoning_2017} uses enter-capabilities to achieve this.
On \trgcm{} we have sealed capabilities to achieve this.
Syntactically, sealed capabilities add two things to the capability machine: Sets of seals $\seal{\sigma_\var{base},\sigma_\var{end},\sigma}$ and sealed capabilities $\sealed{\sigma,\vsc}$.
% seals
A set of seals consists of a range of available seals $[\sigma_\var{base},\sigma_\var{end}]$ and the current seal $\sigma$ which is represented by a natural number.
% sealed caps
A sealed capability consists of a sealable $\vsc$ and the seal $\sigma$ it has been sealed with.
The sealables are the sets of seals and the capabilities, and we refer to the set of them as $\SealableCaps$.
The system native tokens $\Cap$ on \trgcm{} are the sealables and the sealed capabilities.

@@

% Note about them vs us, we do nothing that they couldn't do
In the description of the StackToken calling scheme, it has sometimes been in terms of ``them vs us''.
This may have created the impression of an asymmetric calling convention that places a special status on trusted components allowing them to protect themselves against adversaries.
However, \stktokens{} is a modular calling scheme no restriction is put on adversarial components that we do not expect trusted components to meet.
This means that any component can ensure WBCF and LSE by employing \stktokens{}.
% KJAA: ^-- Assuming that there is a global stack address capability, no? Can I "suddenly" begin to impose \stktokens{}?

% Summary of CC
In the this section, we have described our proposed calling convention, \stktokens{}. The measures taken are:
\begin{enumerate}
\item \label{item:check-stkb} Check the base address of the stack capability before and after calls
\item \label{item:non-empty-sf} Make sure that local stack frames are non-empty
\item \label{item:return-data} Create token and data return capability on call split the stack capability in two to get a stack capability for you local stack frame and a stack capability for the unused part of the stack. The stack capability for your local stack frame is sealed and used for the data part of the return pair.
\item \label{item:return-code} Create code return capability on call Seal the old program pointer.
\item Reasonable use of seals return seals are only used to seal old program pointers, all return seals are only used for one call site, and return seals are not leaked.
\end{enumerate}
Item~\ref{item:check-stkb}-\ref{item:return-code} are captured by the code in Figure~\ref{fig:call-code} with the exception of checking stack base before calls. We do not include this check because it only needs to happen once between two calls which means that the check after a call suffices if the base of the stack pointer is not changed subsequently.

@@

Other than that, code memory only contains instructions in the for of integers.

@@

% How a program is lifted to an executable configuration
Given a program as defined in Definition~\ref{def:program-and-context}, we want to be able to execute it which means that we have to lift it to an executable configuration.
When we lift a program to an executable configuration, we need to provide it a stack in order for \stktokens{} to work.
The relation $(\comp_0, c_{\mathrm{main},c}, c_{\mathrm{main},d}) \rightsquigarrow \Phi$ lifts a component with a main to an executable configuration.
It works almost the same on \trgcm{} and \srccm{}.
On both machines a stack that contains all zeroes is added.
On \trgcm{} it is added as part of the memory along with the data and code memory.
On \srccm{} it is added as the free stack in the configuration, and the initial stack is empty as no calls have been made.
The component needs access to the stack, so a stack pointer is added to the register file in $\rstk$.
On \trgcm{} this is just a linear read-write capability, but on \srccm{} it is the representation of a stack pointer.
The entry point of the program is specified by main, so the two capabilities are unsealed (they must have the same seal) and placed in the $\pcreg$ and $\rdata$ registers.
The remainder of the registers contain zero.

Contextual equivalence roughly says that two components behave the same no matter what context we plug them into.
%The remaining defintions
\begin{definition}[Plugging a component into a context]
  When $\var{comp'}$ is a context for component $\var{comp}$ and $\var{comp}' \bowtie \var{comp} \rightsquigarrow \Phi$, 
  then we write $\plug{\var{comp'}}{\var{comp}}$ for the execution configuration $\Phi$.
\end{definition}
\begin{definition}[\trgcm{} and \srccm{} contextual equivalence]
  \label{def:contextual-equivalence}
  ~
  \begin{description}
  \item[On \srccm{}], we define that $\src{\comp_1 \sconeq \comp_2}$ iff
  \begin{equation*}
    \forall \src{\context} \ldotp  \wdjud[\emptyset]{\src{\context}} \Rightarrow \src{\plug{\context}{\comp_1} \sterm{\ta[,1],\stkb_1}} \Leftrightarrow \src{\plug{\context}{\comp_2} \sterm{\ta[,2],\stkb_2}}
  \end{equation*}
  with $\src{\ta[,i]} = \src{\dom(\comp_i.\mscode)}$.
  \item[On \trgcm{}], we define that $\trg{\comp_1 \tconeq \comp_2}$ iff
  \begin{equation*}
    \forall \trg{\context} \ldotp \wdjud[\emptyset]{\trg{\context}} \Rightarrow \trg{\plug{\context}{\comp_1} \term} \Leftrightarrow \trg{\plug{\context}{\comp_2} \term}
  \end{equation*}
\end{description}
where $\Phi\sterm[i]{\src{\ta,\stkb}} \text{ iff } \Phi \nstep[i]{\src{\ta,\stkb}} \halted \quad$ and $\quad \Phi\sterm{\src{\ta,\stkb}} \defeq \exists i \ldotp \sterm[i]{\src{\ta,\stkb}}$
\end{definition}
With the above defined, we are almost ready to state our full-abstraction, and all that remains is the compiler we claim to be fully-abstract.
We only care about the well-formed components, and they sport none of the new syntactic constructs \srccm{} adds to \trgcm{}.
This means that the compilation from \srccm{} components to \trgcm{} components is simply the identity function.
% Full abstraction thm
\todo[inline]{Look at coloring in these theorems. Why are all components and contexts blue?}
\begin{theorem}
  \label{thm:full-abstraction}
  For reasonable, well-formed components $\comp_1$ and $\comp_2$, we have
  \begin{gather*}
    \src{\comp_1} \sconeq \src{\comp_2} \quad \Leftrightarrow \quad    \src{\comp_1} \tconeq \src{\comp_2}
  \end{gather*}
\end{theorem}
Readers unfamiliar with fully-abstract compilation may wonder why Theorem~\ref{thm:full-abstraction} proves that \stktokens{} guarantees LSE and WBCF.
Generally speaking, behavioral equivalences are preserved and reflected by fully-abstract compilers.
This means that any property the source language has must somehow be there after compilation whether or not it is a property of the target language.
If the source language has a property that the target language doesn't have, then a compiled source program must use the available target language features to emulate the source language property in a way that it behaviorally matches exactly.
In our case, LSE and WBCF was built into the semantics of \srccm{}, but they are not properties of \trgcm{}.
In order to enforce these properties, components on \trgcm{} use \stktokens{}.
Theorem~\ref{thm:full-abstraction} proves that \stktokens{} enforces these properties in a way that behaviorally matches \srccm{} which means that it enforces LSE and WBCF.
\todo[inline]{Consider writing a bit more about compiler correctness and contextual equivalence preservation.}

@@

\subsubsection{Code region}
The code region is a central region to the logical relation used to model the code memory of a component.
It is especially interesting because it specifies what the return and closure seals in a component can be used to seal.
The code region is defined as follows:
\[
  \codereg{\sigrets,\sigcloss,\mscode,\gc} \defeq (\pure,
  H^\mathrm{code,\square} \; \sigrets \; \sigcloss \; \mscode \; \gc,
  H^\mathrm{code}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc)
\]
The code region is $\pure$ which makes it persistent in future worlds and reflects the fact that it is addressed by normal capabilities.
The memory relation $H^\mathrm{code,\square} \; (\dots)$ is very selective and only accepts the pair $(\mscode,\mscode)$ and only on the following conditions: The code memory $\mscode$ must be well-formed according to $\vdash$.
Further, all the words contained in $\mscode$ must be non-linear and in the value relation, but as we will see later we have two value relations, a trusted and an untrusted, and the value relation used depends on whether $\mscode$ is trusted.
For now it suffices to know that the untrusted value relation contains everything that untrusted code can safely have.
The trusted value relation includes everything that is in the untrusted value relation, but also the things that are not safe to pass away in a call, e.g.\ return seals.
If the addresses of $\mscode$ are in $\ta$, then the trusted value relation is used, and if $\mscode$ is disjoint with $\ta$, then the untrusted value relation is used.
Further, if $\ta$ is untrusted, then $\sigrets$ has to be empty which means that $\mscode$ cannot contain return seals.

@@

the seal interpretation function $h^\mathrm{code,\square}_\sigma \; (\dots)$ in the code region dictates the return seals and closure seals can be used to seal.
the return seals can only be used to seal return pointers, but only when they actually represent meaning full returns.
for instance, a code return pointer should actually be associated with a trusted call, i.e.\ it should point to the address just after a call.
the corresponding capability on \trgcm{} should point to the address just after the \texttt{xjmp} in the call code (figure~\ref{fig:call-code}) as it needs to do a couple of things to complete the call safely.
further, the call they are associated with has to be the call that uses the seal in question.
the code return pointer is not linear which means that it can be reused which is fine as it can only be used to return from the same call.
on the other hand, the data return pointers are linear which is what prevents reuse of a return pair.
multiple nested calls from the same trusted call will result in multiple stack frames that are each sealed with the same return seal.
the seal interpretation function should allow a data return pointer for any of those pointers, so it simply requires that there exists a region $\stareg[(\ms_S,\ms_T),(\ta,\stkb)]{\spao,\square}$ (a region that only accepts $(\ms_S,\ms_T)$ and requires the contents to be in the untrusted value relation) in the part of the world that governs the call stack.
The data return pointer should point to that stack frame.
A region in the world for the call stack is also associated with a return address, and it should be the return address of the call that uses the return seal in question.
\todo[inline]{Consider writing something about how this relates to prove? We have to show that there is a stack frame, but we can rely on it when we receive a capability with the correct seal.}
  H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; (\ta,\stkb,\gsigrets,\gsigcloss) \; \sigma \; \hat{W}= \\
  \begin{array}[t]{l}
      \npair{\left(\retptrc(\baddr,\eaddr,\aaddr'+\calllen),((\rx,\normal),\baddr,\eaddr,\aaddr)\right)} \mid 
        \sigrets \subseteq \gsigrets \tand \\
        \quad\dom(\mscode) \subseteq \ta \tand 
        \decInstr{\mscode([\aaddr',\aaddr' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}} \tand \\
        \quad\aaddr = \aaddr' + \retoffset \tand \mscode(\aaddr'+\offpc) = \seal{\sigma_b,\sigma_e,\sigma_b} \tand\\
        \quad \sigma = \sigma_b + \offsigma \in \sigrets \tand
        \lbrack \aaddr',\aaddr' + \calllen -1 \rbrack \subseteq \lbrack \baddr, \eaddr \rbrack
      \right\} \cup \\
      \npair{(\retptrd(\baddr,\eaddr),((\rw,\linear),\baddr,\eaddr,\baddr-1))} \mid
        \sigrets \subseteq \gsigrets \tand 
        \dom(\mscode) \subseteq \ta \tand\\
        \quad \exists r \in \addressable{\linear,\pwpriv[\xi(\hat{W})]},\ms_S,\ms_T \ldotp\\
        \qquad\pwpriv[\xi(\hat{W})](r).H \nequal (\stareg[(\ms_S,\ms_T),(\ta,\stkb)]{\spao,\square}, \aaddr'+\calllen) \tand \\
        \qquad \dom(\ms_S) = \dom(\ms_T) = [\baddr,\eaddr] \tand\\
        \qquad \decInstr{\mscode([\aaddr',\aaddr' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}} \tand \\
        \qquad \mscode(\aaddr'+\offpc) = \seal{\sigma_b,\sigma_e,\sigma_b} \tand \sigma = \sigma_b + \offsigma \in \sigrets
    \right\} \\
  \end{array}\\
    \text{ if } \sigma \in \sigrets
We leave out the formal definition of $H^\mathrm{code,\square}_\sigma \; (\dots)$ for $\sigma \in \sigcloss$ and provide an informal description.
What closure seals can be used for depends on whether the code is trusted.
If the code is untrusted, i.e.\ $\dom(\mscode) \# \ta$, then the seal can be used for everything in the untrusted value relation can be sealed which correspond to everything the code has access to.
On the other hand, if the code is trusted, then it depends on whether the sealable in question is executable.
If it is executable, then it can be in the trusted value relation because we want to allow sealing of capabilities for the trusted code; but if it isn't executable, then the sealable has to be in the untrusted value relation.

@@

\subsubsection{Expression relations and friends}
The expression relation $\mathcal{E}$ in this logical relation contains pairs of capabilities that can safely be used for execution with respect to the give world.
That is when capabilities are plugged into configurations with related register files  and related memory relative to the world, then the executions observably behave the same way.
% the other expression relation
With sealed capabilities in the mix, we will also need to be able to say something similar to the above but with a specific data capability in the register file.
To this end, we have the \texttt{xjmp}-expression relation $\mathcal{E}_{\mathrm{xjmp}}$ that relates two pairs of capabilities and requires that they are safe to use for the \texttt{xjmp} instruction.
  % \begin{multline*}
  %   \lre(W)= \\
  %   \left\{ \begin{array}{l}
  %     \npair{\stpair[.]{v_{c,S}}{v_{c,T}}} | \\
  %     \quad\forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk}, W_\lrrs , W_\lrm \ldotp \\
  %     \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrrs ) \tand \memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \tand\\
  %     \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)} \tand \Phi_S' = \Phi_S \updReg{\pcreg}{v_{c,S}} \tand\\
  %     \qquad\Phi_T = (\ms_T,\reg_T) \tand \Phi_T' = \Phi_T\updReg{\pcreg}{v_{c,T}} \tand W \oplus W_\lrrs \oplus W_\lrm\\
  %     \qquad\Rightarrow\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
  %   \end{array}
  %   \right\}
  % \end{multline*}
  \lrexj(W) =
  \\\left\{\begin{array}{l}
      \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} | \\
      \quad \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk}, W_\lrrs , W_\lrm \ldotp \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(\{\rdata\}) (W_\lrrs ) \tand \memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \tand \\
      \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)} \tand \Phi_T = (\ms_T,\reg_T) \tand W \oplus W_\lrrs \oplus W_\lrm \text{ is defined }\\
      \qquad\Rightarrow \exists \Phi_S',\Phi_T'\ldotp \Phi_S' = \src{\var{xjmpRes}}(v_{c,S},v_{d,S},\Phi_S) \tand\\
      \quad\qquad\Phi_T' = \xjmpres{v_{c,T},v_{d,T},\Phi_T}\tand\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
    \right\}
% register file relation
The register-files relation $\lrr(\{\rdata\}) (W_\lrrs )$ relates register files when their registers, with register $\rdata$ and $\pcreg$ as the exception, contain words related in the untrusted value relation.
% memory relation
A memory on \trgcm{} $\ms_T$ is related to a heap, call stack and free stack on \srccm{} if the following is possible: $\ms_T$ can be split in three disjoint parts.
One part relates to $\ms_S$ with respect to the heap world in the standard way, i.e.\ the two memories can be partitioned, so they satisfy all the regions of the heap world.
The second part should relate to the free stack $\ms_\stk$ also in the standard way, but with respect to the free stack world.
The final part relates to the call stack $\stk$ which means that it can be further split into parts that each are related to one of the stack frames of $\stk$ with respect to the call stack world.
The partition must be done in a way that preserves the order of the stack frames in $\stk$.
% , so the top stack frame relates to a part of memory where all the other parts are above in the address space, the second stack frame relates to a part of memory where all the other parts are above in the address space with the exception of the topmost part, and so on.
% Further, all stack frames should be in addresses above $\stkb$.
\extend{Write about the particulars of the three memory satisfaction: heap relation makes sure only one interpretation for each seal. Free stack $\stkb$}
The \texttt{xjmp} expression relation requires register files and memories related under different worlds, namely $W_\lrrs$ and $W_\lrm$, that are related with $\oplus$.
This means that the two worlds have the same regions, but distribute the ownership of partial regions between them.
By doing so, they make sure that for any part of memory only one of them can have a linear capability it.
The two pairs of capabilities related by $\lrexj$ are plugged into their respective configurations using the $\xjmpres{}$ function, so it corresponds to how an $\texttt{xjmp}$ would insert them.
% observation relation

>>>>

\input{../preamble}
% Paper specific redefinitions of commands
\renewcommand{\MemSeg}{\shareddom{MemSeg}}
\renewcommand{\Reg}{\shareddom{RegFile}}
\renewcommand{\RegName}{\shareddom{RegName}}
\renewcommand{\decInstr}[1]{\plainfun{decode}{#1}}
\renewcommand{\updPcAddr}[1]{\plainfun{updPc}{#1}}
\renewcommand{\linCons}[1]{\plainfun{linClear}{#1}}
\renewcommand{\nonExec}[1]{\plainfun{nonExec}{#1}}
\renewcommand{\perm}{\var{p}}
\renewcommand{\SealableCaps}{\shareddom{Sealables}}
\renewcommand{\Cap}{\shareddom{NatTok}}
\renewcommand{\rretc}{\mathrm{r}_{\mathrm{rcode}}}
\renewcommand{\rretd}{\mathrm{r}_{\mathrm{rdata}}}
\renewcommand{\comp}{\var{comp}}
\renewcommand{\memSatStack}[3][n]{\npair[#1]{#2} \in \typesetlr{S}(#3)}
\renewcommand{\memSatFStack}[3][n]{\npair[#1]{#2} \in \typesetlt{F}(#3)}

@@

\newcommand{\trgcm}{\textsc{LCM}}
\newcommand{\srccm}{\textsc{oLCM}}

@@

\todo[inline]{Add itemized contributions}

\paragraph{Outline} Blabla

@@

%%% Seals
% KJAA: Here I am still missing an intuition of what a seal 'is' -- why the range, why the seal as an 'entity'?

Any reasonable capability machine needs a way to set up boundaries between security domains as well as a way to cross the boundaries in a way where each domain retains their authority.
%The M-Machine~\citep{Dally1997Memo59} inspired capability machine in \citet{skorstengaard_reasoning_2017} uses enter-capabilities to achieve this.
On \trgcm{} we have sealed capabilities to achieve this.
Syntactically, sealed capabilities add two things to the capability machine: Sets of seals $\seal{\sigma_\var{base},\sigma_\var{end},\sigma}$ and sealed capabilities $\sealed{\sigma,\vsc}$.
% seals
A set of seals consists of a range of available seals $[\sigma_\var{base},\sigma_\var{end}]$ and the current seal $\sigma$ which is represented by a natural number.
% sealed caps
A sealed capability consists of a sealable $\vsc$ and the seal $\sigma$ it has been sealed with.
The sealables are the sets of seals and the capabilities, and we refer to the set of them as $\SealableCaps$.
The system native tokens $\Cap$ on \trgcm{} are the sealables and the sealed capabilities.

@@

% Note about them vs us, we do nothing that they couldn't do
In the description of the StackToken calling scheme, it has sometimes been in terms of ``them vs us''.
This may have created the impression of an asymmetric calling convention that places a special status on trusted components allowing them to protect themselves against adversaries.
However, \stktokens{} is a modular calling scheme: no restriction is put on adversarial components that we do not expect trusted components to meet.
This means that any component can ensure WBCF and LSE by employing \stktokens{}.
% KJAA: ^-- Assuming that there is a global stack address capability, no? Can I "suddenly" begin to impose \stktokens{}?

% Summary of CC
In the this section, we have described our proposed calling convention, \stktokens{}. The measures taken are:
\begin{enumerate}
\item \label{item:check-stkb} Check the base address of the stack capability before and after calls
\item \label{item:non-empty-sf} Make sure that local stack frames are non-empty
% KJAA: There's a comma (or something!) missing below. 
\item \label{item:return-data} Create token and data return capability on call, split the stack capability in two to get a stack capability for your local stack frame, and a stack capability for the unused part of the stack. The stack capability for your local stack frame is sealed and used for the data part of the return pair.
  % KJAA: Same with the last two items
\item \label{item:return-code} Create code return capability on call Seal the old program pointer.
\item Reasonable use of seals return seals are only used to seal old program pointers, all return seals are only used for one call site, and return seals are not leaked.
\end{enumerate}
Item~\ref{item:check-stkb}-\ref{item:return-code} are captured by the code in Figure~\ref{fig:call-code} with the exception of checking stack base before calls. We do not include this check because it only needs to happen once between two calls which means that the check after a call suffices if the base of the stack pointer is not changed subsequently.

@@

Other than that, code memory only contains instructions in the form of integers.

@@

% How a program is lifted to an executable configuration
Given a program as defined in Definition~\ref{def:program-and-context}, we want to be able to execute it, meaning we have to lift it to an executable configuration.
When we lift a program to an executable configuration, we need to provide it a stack in order for \stktokens{} to work.
The relation $(\comp_0, c_{\mathrm{main},c}, c_{\mathrm{main},d}) \rightsquigarrow \Phi$ lifts a component with a main to an executable configuration.
It works almost the same on \trgcm{} and \srccm{}.
On both machines a stack that contains all zeroes is added.
On \trgcm{} it is added as part of the memory along with the data and code memory.
On \srccm{} it is added as the free stack in the configuration, and the initial stack is empty as no calls have been made.
The component needs access to the stack, so a stack pointer is added to the register file in $\rstk$.
On \trgcm{} this is just a linear read-write capability, but on \srccm{} it is the representation of a stack pointer.
The entry point of the program is specified by main, so the two capabilities are unsealed (they must have the same seal) and placed in the $\pcreg$ and $\rdata$ registers.
The remainder of the registers contain zero.

Contextual equivalence roughly says that two components behave the same no matter what context we plug them into.
%The remaining defintions
\begin{definition}[Plugging a component into a context]
  When $\var{comp'}$ is a context for component $\var{comp}$ and $\var{comp}' \bowtie \var{comp} \rightsquigarrow \Phi$, 
  then we write $\plug{\var{comp'}}{\var{comp}}$ for the execution configuration $\Phi$.
\end{definition}
\begin{definition}[\trgcm{} and \srccm{} contextual equivalence]
  \label{def:contextual-equivalence}
  ~
  \begin{description}
  \item[On \srccm{}], we define that $\src{\comp_1 \sconeq \comp_2}$ iff
  \begin{equation*}
    \forall \src{\context} \ldotp  \wdjud[\emptyset]{\src{\context}} \Rightarrow \src{\plug{\context}{\comp_1} \sterm{\ta[,1],\stkb_1}} \Leftrightarrow \src{\plug{\context}{\comp_2} \sterm{\ta[,2],\stkb_2}}
  \end{equation*}
  with $\src{\ta[,i]} = \src{\dom(\comp_i.\mscode)}$.
  \item[On \trgcm{}], we define that $\trg{\comp_1 \tconeq \comp_2}$ iff
  \begin{equation*}
    \forall \trg{\context} \ldotp \wdjud[\emptyset]{\trg{\context}} \Rightarrow \trg{\plug{\context}{\comp_1} \term} \Leftrightarrow \trg{\plug{\context}{\comp_2} \term}
  \end{equation*}
\end{description}
where $\Phi\sterm[i]{\src{\ta,\stkb}} \text{ iff } \Phi \nstep[i]{\src{\ta,\stkb}} \halted \quad$ and $\quad \Phi\sterm{\src{\ta,\stkb}} \defeq \exists i \ldotp \sterm[i]{\src{\ta,\stkb}}$
\end{definition}
With the above defined, we are almost ready to state our full-abstraction, and all that remains is the compiler we claim to be fully-abstract.
We only care about the well-formed components, and they sport none of the new syntactic constructs \srccm{} adds to \trgcm{}.
This means that the compilation from \srccm{} components to \trgcm{} components is simply the identity function.
% Full abstraction thm
\begin{theorem}
  \label{thm:full-abstraction}
  For reasonable, well-formed components $\comp_1$ and $\comp_2$, we have
  \begin{gather*}
    \src{\comp_1} \sconeq \src{\comp_2} \quad \Leftrightarrow \quad    \src{\comp_1} \tconeq \src{\comp_2}
  \end{gather*}
\end{theorem}
Readers unfamiliar with fully-abstract compilation may wonder why Theorem~\ref{thm:full-abstraction} proves that \stktokens{} guarantees LSE and WBCF.
Generally speaking, behavioral equivalences are preserved and reflected by fully-abstract compilers.
This means that any property the source language has must somehow be there after compilation whether or not it is a property of the target language.
If the source language has a property that the target language doesn't have, then a compiled source program must use the available target language features to emulate the source language property in a way that it behaviorally matches exactly.
In our case, LSE and WBCF was built into the semantics of \srccm{}, but they are not properties of \trgcm{}.
In order to enforce these properties, components on \trgcm{} use \stktokens{}.
Theorem~\ref{thm:full-abstraction} proves that \stktokens{} enforces these properties in a way that behaviorally matches \srccm{} which means that it enforces LSE and WBCF.
\todo[inline]{Consider writing a bit more about compiler correctness and contextual equivalence preservation.}

@@

\subsubsection{Code region}
The code region is a central region to the logical relation used to model the code memory of a component.
It is especially interesting because it specifies what the return and closure seals in a component can be used to seal.
The code region is defined as follows:
\[
  \codereg{\sigrets,\sigcloss,\mscode,\gc} \defeq (\pure,
  H^\mathrm{code,\square} \; \sigrets \; \sigcloss \; \mscode \; \gc,
  H^\mathrm{code}_\sigma \; \sigrets \; \sigcloss \; \mscode \; \gc)
\]
It is a $\pure$ region which makes it persistent in future worlds.
The memory relation $H^\mathrm{code,\square} \; (\dots)$ is very selective and only accepts the pair $(\mscode,\mscode)$ and only on the following conditions: The code memory $\mscode$ must be well-formed according to $\vdash$.
Further, all the words contained in $\mscode$ must be non-linear and in the value relation, but as we will see later we have two value relations, a trusted and an untrusted, and the value relation used depends on whether $\mscode$ is trusted.
For now it suffices to know that the untrusted value relation contains everything that untrusted code can safely have.
The trusted value relation includes everything that is in the untrusted value relation, but also the things that are not safe to pass away in a call, e.g.\ return seals.
If the addresses of $\mscode$ are in $\ta$, then the trusted value relation is used, and if $\mscode$ is disjoint with $\ta$, then the untrusted value relation is used.
Further, if $\ta$ is untrusted, then $\sigrets$ has to be empty which means that $\mscode$ cannot contain return seals.

@@

\begin{multline*}
  H^\mathrm{code,\square}_\sigma \; \sigrets \; \sigcloss \; \mscode \; (\ta,\stkb) \; \sigma \; \hat{W}= \\
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
      \npair{\left(\retptrc(\baddr,\eaddr,\aaddr'+\calllen),((\rx,\normal),\baddr,\eaddr,\aaddr)\right)} \mid 
        \sigrets \subseteq \gsigrets \tand \\
        \quad\dom(\mscode) \subseteq \ta \tand 
        \decInstr{\mscode([\aaddr',\aaddr' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}} \tand \\
        \quad\aaddr = \aaddr' + \retoffset \tand \mscode(\aaddr'+\offpc) = \seal{\sigma_b,\sigma_e,\sigma_b} \tand\\
        \quad \sigma = \sigma_b + \offsigma \in \sigrets \tand
        \lbrack \aaddr',\aaddr' + \calllen -1 \rbrack \subseteq \lbrack \baddr, \eaddr \rbrack
    \end{array}
      \right\} \cup \\
\left\{
    \begin{array}{l}
      \npair{(\retptrd(\baddr,\eaddr),((\rw,\linear),\baddr,\eaddr,\baddr-1))} \mid
        \sigrets \subseteq \gsigrets \tand 
        \dom(\mscode) \subseteq \ta \tand\\
        \quad \exists r \in \addressable{\linear,\pwpriv[\xi(\hat{W})]},\ms_S,\ms_T \ldotp\\
        \qquad\pwpriv[\xi(\hat{W})](r).H \nequal (\stareg[(\ms_S,\ms_T),(\ta,\stkb)]{\spao,\square}, \aaddr'+\calllen) \tand \\
        \qquad \dom(\ms_S) = \dom(\ms_T) = [\baddr,\eaddr] \tand\\
        \qquad \decInstr{\mscode([\aaddr',\aaddr' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}} \tand \\
        \qquad \mscode(\aaddr'+\offpc) = \seal{\sigma_b,\sigma_e,\sigma_b} \tand \sigma = \sigma_b + \offsigma \in \sigrets
    \end{array}
    \right\} \\
  \end{array}\\
    \text{ if } \sigma \in \sigrets\\
\end{multline*}
We leave out the formal definition of $H^\mathrm{code,\square}_\sigma \; (\dots)$ for $\sigma \in \sigcloss$ and provide an informal description.
What closure seals can be used for depends on whether the code is trusted.
If the code is untrusted, i.e.\ $\dom(\mscode) \# \ta$, then the seal can be used for everything in the untrusted value relation can be sealed which correspond to everything the code has access to.
On the other hand, if the code is trusted, then it depends on whether the sealable in question is executable.
If it is executable, then it can be in the trusted value relation because we want to allow sealing of capabilities for the trusted code; but if it isn't executable, then the sealable has to be in the untrusted value relation.

@@

\subsubsection{Expression relations}
\begin{multline*}
  \lrexj(W) =
  \\\left\{\begin{array}{l}
      \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} | \\
      \quad \forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk}, W_\lrrs , W_\lrm \ldotp \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(\{\rdata\}) (W_\lrrs ) \tand \memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \tand \\
      \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)} \tand \Phi_T = (\ms_T,\reg_T) \tand W \oplus W_\lrrs \oplus W_\lrm \text{ is defined }\\
      \qquad\Rightarrow \exists \Phi_S',\Phi_T'\ldotp \Phi_S' = \xjumpResult{v_{c,S}}{v_{d,S}}{\Phi_S} \tand\\
      \quad\qquad\Phi_T' = \xjumpResult{v_{c,T}}{v_{d,T}}{\Phi_T}\tand\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
    \end{array}
    \right\}
\end{multline*}

  % \begin{multline*}
  %   \lre(W)= \\
  %   \left\{ \begin{array}{l}
  %     \npair{\stpair[.]{v_{c,S}}{v_{c,T}}} | \\
  %     \quad\forall n' \leq n, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk}, W_\lrrs , W_\lrm \ldotp \\
  %     \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrrs ) \tand \memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \tand\\
  %     \qquad\Phi_S = \src{(\ms_S,\reg_S,\stk, \ms_\stk)} \tand \Phi_S' = \Phi_S \updReg{\pcreg}{v_{c,S}} \tand\\
  %     \qquad\Phi_T = (\ms_T,\reg_T) \tand \Phi_T' = \Phi_T\updReg{\pcreg}{v_{c,T}} \tand W \oplus W_\lrrs \oplus W_\lrm\\
  %     \qquad\Rightarrow\npair[n']{\left(\Phi_S', \Phi_T' \right)}\in \lro
  %   \end{array}
  %   \right\}
  % \end{multline*}
\[
  \lrol =\{ \npair{\left(\src{\Phi_S},\Phi_T\right)} \mid
  \forall i \leq n \ldotp
    \src{\Phi_S \sterm[i]{\ta,\stkb}} \Rightarrow \Phi_T \trg{\term} \}
\]
\[
  \lror = \{ \npair{\left(\src{\Phi_S},\Phi_T\right)} \mid
  \forall i \leq n \ldotp 
    \Phi_T \trg{\term[i]} \Rightarrow \src{\Phi_S \sterm{\ta,\stkb}} \}
\]
